The impact of forest management on the temperature sensitivity of organic matter turnover

### 2024-11-14 Manuscript_draft/Draft.Rmd
disc

Our analyses revealed the three variables that explained most of the variation of Q10 were related to i) the quality of substrate (i.e., nitrogen content as limiting nutrient in forest), ii) the microorganisms, in particular, fungal to bacteria ratio and iii) the soil temperature. Our results indicate that SOM decomposition not only depends on the substrate biochemistry but also on the ability of the existing microbial community to decompose the available substrate. This is in partial agreement with a recent global scale study stating that soil microbiomes are the main players governing the responses of soil heterotrophic respiration to temperature, and secondly substrate quantity and biochemical recalcitrance (Sáez-Sandino et al 2023). Since total microbial biomass did not correlated with total nitrogen, the observed effect of nitrogen might be related to an increased in mineral nitrogen.
Compared to controls, fungal and bacteria biomass decreased in both thinning and clear-cut indicating a stronger decrease in ectomycorrhizal fungi compared to root-fungi associated bacteria. In forest, the role of fungi, especially of ectomycorrhizal fungi in decomposing SOM while mining for nutrients. The stronger decrease in ectomycorrhizal fungi, might have increased sensitivity to temperature linked to reduced fungal activity. The decrease This could   The higher increase in fungal biomass compared to bacteria in the treatments with slash indicate a faster colonization of saprotrophic fungi in litter. An probably temperatre sensitivity is controlled by a reduced number of taxa with a high abundance (Sáez-Sandino et al 2023). Diversity metrics would give more insights about that.

>>>>

Our analyses revealed the three variables that explained most of the variation of Q10 were related to i) the quality of substrate (i.e., nitrogen content as limiting nutrient in forest), ii) the microorganisms, in particular, fungal to bacteria ratio and iii) the soil temperature. Our results indicate that SOM decomposition not only depends on the substrate biochemistry but also on the ability of the microbial community to decompose the available substrate. This is in partial agreement with a recent global-scale study stating that soil microbiomes are the main players governing the responses of soil heterotrophic respiration to temperature, and secondly substrate quantity and biochemical recalcitrance (Sáez-Sandino et al 2023). Since total microbial biomass did not correlate with total nitrogen, the observed effect of nitrogen might be related to an increased in mineral nitrogen. This would alleviate the nitrogen limitation normally present in forests and favouring decomposition.

Compared to controls, fungal and bacteria biomass decreased in both thinning and clear-cut indicating a stronger decrease in ectomycorrhizal fungi compared to root-fungi associated bacteria. In forest, the role of fungi, especially of ectomycorrhizal fungi in decomposing SOM while mining for nutrients. The stronger decrease in ectomycorrhizal fungi, might have increased sensitivity to temperature linked to reduced fungal activity. The decrease This could   The higher increase in fungal biomass compared to bacteria in the treatments with slash indicate a faster colonization of saprotrophic fungi in litter. An probably temperatre sensitivity is controlled by a reduced number of taxa with a high abundance (Sáez-Sandino et al 2023). Diversity metrics would give more insights about that.
